\cvsection{Work Experience}

\begin{cventries}

  \cventry
    {Tech Lead \& Senior PHP Fullstack Developer} % Job title
    {\href{https://dnj.co.ir}{DNJ Co.}} % Organisation
    {Isfahan, Iran} % Location
    {Oct 2022 - Sep 2024} % Date(s)
    {
      \begin{cvitems}
        \item {Lead a team of \textbf{8 developers} in delivering high-quality, scalable web applications for clients using \textbf{Symfony}, \textbf{Laravel}, \textbf{Vue.js}, and \textbf{React}, with a strong focus on open-source contributions.}
        \item {Developed an internal portal for a client, enabling \textbf{500 employees} to manage tasks and workflows daily, enhancing productivity and operational transparency.}
        \item {Modernized a legacy client website into a \textbf{14-language Laravel platform} with \textbf{Octane (Swoole)} and \textbf{NuxtJS}, handling \textbf{1,000,000 requests per hour} and built with \textbf{Docker} for efficient, reliable deployments.}
        \item {Actively utilize \textbf{AWS Lambda}, \textbf{AWS S3}, \textbf{Azure Serverless}, and \textbf{Azure Kubernetes} to build scalable, serverless solutions aligned with modern cloud standards.}
        \item {Built and maintain open-source libraries accessible on GitHub under the \textbf{\href{https://github.com/dnj}{\faGithubSquare\acvHeaderIconSep @dnj}} organization, contributing reusable tools for the developer community.}
        \item {Maintain a PHPUnit \textbf{strict 80\% minimum test coverage} across projects, ensuring code reliability, performance, and maintainability.}
      \end{cvitems}
    }

  \cventry
    {Senior PHP Developer} % Job title
    {\href{https://www.hinics.com/}{Sepehr Electric}} % Organisation
    {Isfahan, Iran} % Location
    {Apr 2022 - Oct 2022} % Date(s)
    {
      \begin{cvitems}
        \item {Developed a high-performance backend for an IoT timer device using \textbf{Laravel}, \textbf{Swoole}, and \textbf{WebSocket} for real-time communication, handling over \textbf{67,000 IoT devices} and supporting \textbf{2,000 mobile app users}.}
        \item {Implemented \textbf{Protobuf} as the data format for efficient, lightweight communication suited to real-time IoT demands.}
        \item {Implemented a \textbf{CI/CD pipeline} on GitHub Actions that completes testing, builds container images, and deploys to \textbf{GCP} in under \textbf{5 minutes}, enabling rapid and reliable production updates.}
      \end{cvitems}
    }

  \cventry
    {PHP Developer} % Job title
    {Taxi Paytakht} % Organisation
    {Isfahan, Iran} % Location
    {May 2019  - Nov 2021} % Date(s)
    {
      \begin{cvitems}
        \item {Developed a backend for an online taxi service using \textbf{Symfony}, achieving \textbf{83\% test coverage} and delivering reliable, high-performance APIs.}
        \item {Implemented a \textbf{routing service} using \textbf{OpenStreetMap} data, enabling taxi drivers to find the fastest route from source to destination.}
        \item {Designed and documented \textbf{RESTful APIs} in \textbf{OpenAPI} format, facilitating smooth integration for mobile app developers.}
        \item {Built and deployed a fully automated \textbf{CI/CD pipeline} on \textbf{GitLab}, streamlining testing, Docker image creation, and \textbf{Kubernetes deployment}.}
        \item {Scaled the application to support \textbf{500 trips per hour}, serving \textbf{1,100+ concurrent users} at peak times.}
      \end{cvitems}
    }
  
  \cventry
    {Full-Stack Developer} % Job title
    {Aroseirani} % Organisation
    {Mashhad, Iran (Remote)} % Location
    {Apr 2017 - Mar 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contracted with INAF Company to work on the \href{https://aroseirani.com}{\underline{AroseIrani.com}} project, a directory listing website for Local wedding-related businesses.}
        \item {Developed the website using a custom \textbf{PHP} framework, HTML, CSS, and jQuery.}
        \item {Implemented a \textbf{RESTful API} and thoroughly documented it for Android developers.}
        \item {Utilized \textbf{MySQL} for database management.}
        \item {Developed a TelegramBot for administrative and notification purposes.}
        \item {Designed and implemented a feature-rich admin panel for extensive website customization.}
        \item {Utilized \textbf{FFMPEG} to add watermarks to videos and re-render them in different qualities for improved user experience.}
      \end{cvitems}
    }

  \cventry
    {Founder \& Lead PHP Developer} % Job title
    {\href{https://jeyserver.com}{JeyServer}} % Organisation
    {Isfahan, Iran} % Location
    {Mar 2014 - Feb 2017} % Date(s)
    {
      \begin{cvitems}
        \item {Founded a web hosting company and developed \href{https://jalno.ir/en/}{Jalno}, a custom open-source PHP framework, to power the infrastructure, with several components still actively maintained and available on \href{https://github.com/jeyserver}{GitHub}.}
        \item {Led a team of \textbf{6 developers}, scaling the platform to support \textbf{12,000 WordPress} sites and processing \textbf{141,000 orders} over three years.}
        \item {Developed an advanced, fully automated OS installation system for \textbf{Linux/Windows} on VPS (\textbf{VMware ESXi}) and bare metal servers, a solution that remains highly regarded in the hosting industry.}
        \item {Hosted all assets on \textbf{AWS S3} for efficient, scalable file storage and utilized \textbf{Docker} for streamlined deployments, ensuring consistency across environments.}
      \end{cvitems}
    }
  
  \cventry
    {Founder \& Lead PHP Developer} % Job title
    {DChat} % Organisation
    {Isfahan, Iran} % Location
    {May 2011 - Feb 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conceptualized and developed DChat, a Chatroom application from 2012 to 2014. Utilized \textbf{PHP}, \textbf{jQuery}, and \textbf{MySQL} to create a high-speed, efficient platform tailored for ultra-low speed connections.}
        \item {Managed deployment of \textbf{over 500} instances of DChat, which garnered viral attention, serving more than \textbf{30,000 concurrent end users} across \textbf{+20 servers}.}
        \item {Developed rich features including public/private chats, stickers, file attachments, and robust admin functionalities.}
        \item {Recognized the need for a custom billing system and engineered an exclusive application to manage chatrooms and import data from the legacy script “E-Chat”. This billing system, also PHP-based, effectively managed all 23 servers.}
        \item {Introduced a feature named “Feed”, akin to modern-day Instagram, allowing users to post images, videos, text, and audio. Addressed storage limitations by implementing an object-storage solution similar to \textbf{AWS S3}.}
      \end{cvitems}
    }

\end{cventries}
