\cvsection{Work Experience}

\begin{cventries}

  \cventry
    {Co-Founded and Led Growing Web Hosting Startup} % Job title
    {\href{https://dnj.co.ir}{Dade Negar Jey}} % Organisation
    {Isfahan, Iran} % Location
    {Mar 2014 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Spearheaded the launch and ongoing growth of \href{https://www.jeyserver.com/}{\underline{JeyServer.com}} (2014), a web hosting provider, leading a talented team of \textbf{12 individuals}. We currently support over \textbf{12,000 WordPress sites} on a daily basis, highlighting our expertise in web hosting solutions.}
        \item {Developed a custom billing system (Jalno) replicating the functionality of WHMCS, ensuring a seamless customer experience.}
        \item {Established a robust Linux shared hosting platform by integrating cPanel and DirectAdmin with our in-house billing system, serving multiple corporate clients.}
        \item {Built an automated VPS provisioning system leveraging VMware ESXi servers, offering functionalities similar to SolusVM and AutoVM. Our solution empowers us to provide high-quality VPS and dedicated server rentals along with technical support to our corporate customers.}
      \end{cvitems}
    }

  \cventry
    {IOT Full-Stack Software Developer (Contractor)} % Job title
    {Sepehr Electric} % Organisation
    {Isfahan, Iran} % Location
    {Apr 2023 - Oct 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Collaborated with \href{https://www.hinics.com/}{\underline{Hinics}}, an electronics company, to develop a smart and internet-connected relay capable of controlling other devices based on various conditions such as time, temperature, humidity, and manual actions.}
        \item {Designed the device using ESP8266 and created a mobile app for device management via WiFi-Direct, internet, or SMS.}
        \item {Developed an online dashboard for device owners to monitor and manage their devices, with additional support for sales and support teams.}
        \item {Wrote ESP8266 firmware using modern \textbf{C++} code and contributed \href{https://registry.platformio.org/search?q=owner\%3Ayeganemehr}{\underline{some libraries}} to the PlatformIO repository as open source.}
        \item {Developed the mobile application using \textbf{Vue.js} and \textbf{Cordova}, and server backend using Swoole and \textbf{Laravel} to create both \textbf{RESTful API} and a \textbf{Protobuf}-based websocket API.}
        \item {Integrated SMS800 for receiving commands from the app and sending responses.}
      \end{cvitems}
    }

  \cventry
    {Full-Stack Developer (Contractor)} % Job title
    {Egerd} % Organisation
    {Tehran, Iran} % Location
    {Apr 2022 - Nov 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contracted as a Full-Stack Developer at \href{https://egerd.com/}{\underline{Egerd}}, tasked with optimizing website performance and implementing efficient development practices.}
        \item {Received projects with components written in \textbf{Python (Django)}, \textbf{JavaScript (Express)} for backend, and \textbf{Next.js} for the frontend, without any documentation or support from previous developers.}
        \item {Successfully optimized website performance, reducing load time from over 50 seconds to less than 3 seconds.}
        \item {Streamlined server infrastructure, reducing resource requirements from a 32-core CPU, 2 NVMe disks, and 64 GB of RAM to a modest 4 GB RAM and 2 core setup, resulting in significant cost savings.}
        \item {Dockerized the project for improved deployment and management.}
        \item {Implemented CI/CD using GitHub Actions and extensively documented processes for future team members.}
      \end{cvitems}
    }
  
  \cventry
    {Full-Stack Developer} % Job title
    {Aroseirani} % Organisation
    {Mashhad, Iran} % Location
    {Apr 2016 - May 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contracted with INAF Company to work on the \href{https://aroseirani.com}{\underline{AroseIrani.com}} project, a directory listing website for Local wedding-related businesses.}
        \item {Developed the website using a custom \textbf{PHP} framework, HTML, CSS, and JavaScript.}
        \item {Implemented a \textbf{RESTful API} and thoroughly documented it for Android developers.}
        \item {Utilized \textbf{MySQL} for database management.}
        \item {Developed a TelegramBot for administrative and notification purposes.}
        \item {Designed and implemented a feature-rich admin panel for extensive website customization.}
        \item {Utilized \textbf{FFMPEG} to add watermarks to videos and re-render them in different qualities for improved user experience.}
      \end{cvitems}
    }
  
  \cventry
    {Project Lead and Developer} % Job title
    {DChat} % Organisation
    {Isfahan, Iran} % Location
    {May 2011 - Feb 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conceptualized and developed DChat, a Chatroom application from 2012 to 2014. Utilized \textbf{PHP}, \textbf{jQuery}, and \textbf{MySQL} to create a high-speed, efficient platform tailored for ultra-low speed connections.}
        \item {Managed deployment of \textbf{over 500} instances of DChat, which garnered viral attention, serving more than \textbf{30,000 concurrent end users} across \textbf{+20 servers}.}
        \item {Developed rich features including public/private chats, stickers, file attachments, and robust admin functionalities.}
        \item {Recognized the need for a custom billing system and engineered an exclusive application to manage chatrooms and import data from the legacy script “E-Chat”. This billing system, also PHP-based, effectively managed all 23 servers.}
        \item {Introduced a groundbreaking feature named “Feed”, akin to modern-day Instagram, allowing users to post images, videos, text, and audio. Addressed storage limitations by implementing an object-storage solution similar to \textbf{AWS S3}.}
      \end{cvitems}
    }

\end{cventries}
