\cvsection{Work Experience}

\begin{cventries}

  \cventry
    {Tech Lead \& Senior Fullstack Developer} % Job title
    {\href{https://dnj.co.ir}{DNJ Co.}} % Organisation
    {Isfahan, Iran} % Location
    {Oct 2022 - Sep 2024} % Date(s)
    {
      \begin{cvitems}
        \item {Lead a team of \textbf{8 developers} in delivering high-quality, scalable web applications for clients using \textbf{NestJS}, \textbf{ExpressJS}, \textbf{Vue.js}, and \textbf{React}, with a strong focus on open-source contributions.}
        \item {Developed an internal portal for a client, enabling \textbf{500 employees} to manage tasks and workflows daily, enhancing productivity and operational transparency.}
        \item {Modernized a legacy client website into a \textbf{NuxtJS} project, handling \textbf{1,000,000 requests per hour} and built with \textbf{Docker} for efficient, reliable deployments.}
        \item {Actively utilize \textbf{AWS Lambda}, \textbf{AWS S3}, \textbf{Azure Serverless}, and \textbf{Azure Kubernetes} to build scalable, serverless solutions aligned with modern cloud standards.}
        \item {Built and maintain open-source libraries accessible on GitHub under the \textbf{\href{https://github.com/dnj}{\faGithubSquare\acvHeaderIconSep @dnj}} organization, contributing reusable tools for the developer community.}
        \item {Maintain a \textbf{strict 80\% minimum test coverage} across projects, ensuring code reliability, performance, and maintainability.}
      \end{cvitems}
    }

  \cventry
    {Fronend Developer} % Job title
    {\href{https://www.hinics.com/}{Sepehr Electric}} % Organisation
    {Isfahan, Iran} % Location
    {Apr 2023 - Oct 2023} % Date(s)
    {
      \begin{cvitems}
        \item {Developed a hybrid mobile application using \textbf{Vue.js 3} (Composition API) and \textbf{Pinia}, enabling \textbf{2,000 active} users monthly to manage \textbf{67,000} IoT devices via Wi-Fi Direct (local), internet (server-based), and SMS communication.}
        \item {Implemented real-time communication systems with \textbf{WebSocket} for Wi-Fi and internet modes, ensuring seamless interaction, and wrote a custom \textbf{Cordova} plugin to handle SMS-based device control, providing functionality in low-connectivity environments.}
        \item {Optimized and automated workflows by leveraging \textbf{Protobuf} to minimize data size and creating a dynamic, real-time UI. Additionally, built a \textbf{GitHub Workflow} to automate the building and signing of Cordova outputs, streamlining the deployment process.}
      \end{cvitems}
    }
  

  \cventry
    {Full-Stack Developer} % Job title
    {Egerd} % Organisation
    {Tehran, Iran} % Location
    {Apr 2022 - Nov 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contracted as a Full-Stack Developer at \href{https://egerd.com/}{\underline{Egerd}}, tasked with optimizing website performance and implementing efficient development practices.}
        \item {Received projects with components written in \textbf{JavaScript (Express)} for backend, and \textbf{Next.js} for the frontend, without any documentation or support from previous developers.}
        \item {Successfully optimized website performance, reducing load time from over 50 seconds to less than 3 seconds.}
        \item {Streamlined server infrastructure, reducing resource requirements from a 32-core CPU, 2 NVMe disks, and 64 GB of RAM to a modest 4 GB RAM and 2 core setup, resulting in significant cost savings.}
        \item {Dockerized the project for improved deployment and management.}
        \item {Implemented CI/CD using GitHub Actions and extensively documented processes for future team members.}
      \end{cvitems}
    }

  \cventry
    {Frontend Developer} % Job title
    {Taxi Paytakht} % Organisation
    {Isfahan, Iran} % Location
    {May 2019  - Nov 2021} % Date(s)
    {
      \begin{cvitems}
        \item {Developed two mobile applications using \textbf{React.js} and \textbf{Cordova}: a passenger app for trip bookings and a driver app featuring professional GPS integration with advanced battery optimization.}
        \item {These apps supported over \textbf{1,100 concurrent users} and facilitated \textbf{500 trips per hour} during peak operation.}
        \item {Enhanced functionality with cutting-edge technologies, utilizing GPS features for real-time navigation, \textbf{OpenStreetMap} for routing, and robust backend APIs to ensure reliable and efficient trip management.}
        \item {Automated deployment workflows by creating a \textbf{GitHub Workflow} to build and deliver \textbf{Cordova} outputs, significantly reducing manual effort in generating installable app files for production releases.}
      \end{cvitems}
    }
  
  \cventry
    {PHP Full-Stack Developer} % Job title
    {Aroseirani} % Organisation
    {Mashhad, Iran (Remote)} % Location
    {Apr 2017 - Mar 2019} % Date(s)
    {}

  \cventry
    {Founder \& Lead Developer} % Job title
    {\href{https://jeyserver.com}{JeyServer}} % Organisation
    {Isfahan, Iran} % Location
    {Mar 2014 - Feb 2017} % Date(s)
    {
      \begin{cvitems}
        \item {Founded a web hosting company and developed \href{https://jalno.ir/en/}{Jalno}, a custom open-source framework, to power the infrastructure, with several components still actively maintained and available on \href{https://github.com/jeyserver}{GitHub}.}
        \item {Led a team of \textbf{6 developers}, scaling the platform to support \textbf{12,000 WordPress} sites and processing \textbf{141,000 orders} over three years.}
        \item {Developed an advanced, fully automated OS installation system for \textbf{Linux/Windows} on VPS (\textbf{VMware ESXi}) and bare metal servers, a solution that remains highly regarded in the hosting industry.}
        \item {Hosted all assets on \textbf{AWS S3} for efficient, scalable file storage and utilized \textbf{Docker} for streamlined deployments, ensuring consistency across environments.}
      \end{cvitems}
    }
  
  \cventry
    {Founder \& Lead PHP Developer} % Job title
    {DChat} % Organisation
    {Isfahan, Iran} % Location
    {May 2011 - Feb 2014} % Date(s)
    {}

\end{cventries}
